Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-14 paper/paper.tex
first draft of conclusion

>>>>

The problem of identifying subgraph isomorphisms is a hard computation problem
that has many applications in diverse areas. In this paper, we presented a
portfolio of six algorithms from the literature and a novel variant of the \LAD
algorithm. We introduced a set of novel features to characterise subgraph
isomorphism problems and leveraged them to select the most appropriate algorithm
from the portfolio for each instance.

We demonstrated that our portfolio achieves substantial performance improvements
over the single algorithm that has the best performance on our benchmark set. We
showed that combining a portfolio approach with a novel incomplete variant of
\LAD that is able to detect inconsistencies and a presolver boosts performance
even further.
